Formalizing Stack Safety as a Security Property

### 2023-02-02 submission5/core.tex
Nits

In this section we introduce our security property definitions by means
of small code examples, using a simplified set of security-relevent operations for
or calls, returns, and private allocations.
% In this system a value is a pair of a
%word (the ``payload'') and a tag drawn from some set \(\mathcal{T}\).
%\(\mathcal{V} ::= \mathcal{W} \times \mathcal{T}\),
%for some type  of tags to be elaborated later, with \(|(w,t)| = w\).
Figure \ref{fig:main} gives C code and corresponding compiled 64-bit RISC-V code
for a function {\tt main}, which  
takes an argument {\tt secret} and initializes a local variable {\tt sensitive} to contain
potentially sensitive data. 
Then {\tt main} calls another function {\tt f},
and afterward performs a test on {\tt sensitive} to decide whether
to output {\tt secret}.  Since {\tt sensitive} is initialized to 0,
the test should fail, and {\tt main} should instead output the return value of {\tt f}.
Output is performed by writing to the special global {\tt out},
and we assume that such writes are the only observable events in the system.

@@

>>>>

In this section we introduce our security property definitions by means
of small code examples, using a simplified set of security-relevent operations for
or calls, returns, and private allocations.
% In this system a value is a pair of a
%word (the ``payload'') and a tag drawn from some set \(\mathcal{T}\).
%\(\mathcal{V} ::= \mathcal{W} \times \mathcal{T}\),
%for some type  of tags to be elaborated later, with \(|(w,t)| = w\).
Figure \ref{fig:main} gives C code and corresponding compiled 32-bit RISC-V code
for a function {\tt main}, which
takes an argument {\tt secret} and initializes a local variable {\tt sensitive} to contain
potentially sensitive data.
Then {\tt main} calls another function {\tt f},
and afterward performs a test on {\tt sensitive} to decide whether
to output {\tt secret}.  Since {\tt sensitive} is initialized to 0,
the test should fail, and {\tt main} should instead output the return value of {\tt f}.
Output is performed by writing to the special global {\tt out},
and we assume that such writes are the only observable events in the system.

@@

\bcp{Bits missing here!}
